%!TEX root = ./cv.tex
\textbf{Refereed Conference and Workshop Publications}
\begin{enumerate}
\setcounter{enumi}{0}
\item T.Groves, \textbf{N.Namashivayam}, B.Cook, B.Friesen, N.Keen, D.Trebotich,
      N.J.Wright, B.Alverson, D.Roweth, and K.Underwood. \textit{"Not All
      Applications Have Boring Communication Patterns: Profiling Message Matching
      with BMM"}. In Proceedings of Concurrency and Computation: Practice and Experience.
\item \textbf{N.Namashivayam}, S.Mehta, and P.C.Yew. \textit{"Variable-sized 
      Blocks for Locality-aware SpMV"}. In Proceedings of International
        Symposium on Code Generation and Optimization (CGO 2021).
\item \textbf{N.Namashivayam}, B.Long, D.Eachempati, B.Cernohous, and M.Pagel.
      \textit{"A Modern Fortran Interface in OpenSHMEM."}. In Proceedings of
      ACM Transactions on Parallel Computing, August, 2020.
\item \textbf{N.Namashivayam}, B.Cernohous, D.Pou, and M.Pagel.
      \textit{"Introducing Cray OpenSHMEMX - A Modular Multi-Communication Layer
      OpenSHMEM Implementation."}. In Proceedings of Fifth Workshop on OpenSHMEM
      and Related Technologies, August, 2018, Hanover, USA.
\item \textbf{N.Namashivayam}, B.Cernohous, K.Kandalla, D.Pou, J.Robichaux,
      J.Dinan, and M.Pagel.
      \textit{"Symmetric Memory Partitions in OpenSHMEM: A case study with
      Intel KNL"}. In Proceedings of Fourth Workshop on OpenSHMEM and
      Related Technologies: Big Compute and Big Data Convergence, August,
      2017, Annapolis, USA.
\item K.Kandalla, P.Mendygral, N.Radcliffe, B.Cernohous,
      \textbf{N.Namashivayam}, K.McMahon, C.Sadlo and M.Pagel
      \textit{"Current State of the Cray MPT Software Stacks on the Cray XC
      Series Supercomputers"}. In proceedings of Cray User Group Meeting,
      2017, Redmond, USA.
\item \textbf{N.Namashivayam}, D.Knaak, B.Cernohous, N.Radcliffe, and
      M.Pagel.
      \textit{"An Evaluation of Thread-Safe and Contexts-Domains Features in
      Cray SHMEM"}. In Proceedings of Third Workshop on OpenSHMEM and Related
      Technologies: Enhancing OpenSHMEM for Hybrid Environments, August, 2016,
      Hanover, USA.
\item \textbf{N.Namashivayam}, D.Eachempati, D.Khaldi and B.Chapman.
      \textit{"OpenSHMEM as a Portable Communication Layer for PGAS Models - A
      Case Study with Coarray Fortran"}. In Proceedings of IEEE Cluster 2015,
      September, 2015, Chicago, USA.
\item \textbf{N.Namashivayam}, D.Khaldi, D.Eachempati and B.Chapman.
      \textit{"Extending the Strided Communication Interface in OpenSHMEM"}. In
      Proceedings of Second OpenSHMEM Workshop: Experiences, Implementations and
      Tools, August, 2015, Annapolis, USA.
\item D.Knaak, and \textbf{N.Namashivayam}.
      \textit{"Proposing OpenSHMEM Extensions Towards a Future for Hybrid
      Programming and Heterogeneous Computing"}, In Proceedings of Second
      OpenSHMEM Workshop: Experiences, Implementations and Tools, August, 2015,
      Annapolis, USA.
\item \textbf{N.Namashivayam}, S.Ghosh, D.Khaldi, D.Eachempati, and B.Chapman.
      \textit{"Native Mode-Based Optimizations of Remote Memory Accesses in
      OpenSHMEM for Intel Xeon Phi"}, 8th International Conference on Partitioned
      Global Address Space Programming Models (PGAS 2014).
\end{enumerate}

\textbf{Thesis}
\begin{itemize}
\item N.Namashivayam.
      \textit{"OpenSHMEM as an Effective Communication Layer for PGAS Models"}.
      Master's Thesis, University of Houston, October, 2015.
\end{itemize}

\textbf{Other Publications}
\begin{enumerate}
\setcounter{enumi}{0}
\item \textbf{N.Namashivayam}, K. Kandalla, T. White, L.Kaplan, and M. Pagel.
      \textit{"Exploring Fully Offloaded GPU Stream-Aware Message Passing"}.
      arXiv preprint arXiv:2306.15773.
\item \textbf{N.Namashivayam}, K. Kandalla, T. White, N. Radcliffle, L.Kaplan,
      and M. Pagel.
      \textit{"Exploring GPU Stream-Aware Message Passing using Triggered
      Operations"}. arXiv preprint arXiv:2306.15773.
\end{enumerate}


